Finally Tagless, Partially Evaluated

### 2008-10-24 tagless/tagless-final.tex
add a bit to the related work and clean up the notes some more

>>>>

Very recently others have also begun to realize the usefulness of being
able to abstract over higher-kinded types, like our |repr|.
\Citet{moors-generics-higher-kind} illustrate how they have leveraged the 
same power within Scala.  \Citet{HORM08} also uses Scala, yet are clearly
influenced by our work \citep{carette-kiselyov-shan-aplas}
(as they themselves note); where we have concentrated
on multiple efficient interpretations of the same language, they have 
concentrated on composability.
